Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-19 overview.tex
updates in overview

Liveness properties are much harder to specify and check since they apply over entire program executions and not just individual program states. The liveness property that is being checked in the Azure Storage vNext system is that a user-defined $N$ number of extent nodes must be always eventually available with the latest extent.

>>>>

Liveness properties are much harder to specify and check since they apply over entire program executions and not just individual program states. As an example, the liveness property that must be always eventually satisfied in the Azure Storage vNext system is that a user-defined $N$ number of extent nodes must be always eventually available with the latest extent. There was an actual bug in the system, that led this property to fail for some very rare executions. Although this buggy behavior would be observed from time to time during stress testing, there was no way to reproduce the bug. We discuss later in this paper, how we are able to detect and reproduce this bug using our approach.
